---
title: "p8105_hw5_dl3757"
author: "Dang Lin dl3757"
date: "2024-11-15"
output: github_document
---

```{r message = FALSE, warning = FALSE}
library(tidyverse)

set.seed(3757)
```

# Problem 1
```{r message = FALSE, warning = FALSE}
# Write a function to check if there are duplicate birthdays in a group
birthday_sim = function(n) {

  bdays = sample(1:365, size = n, replace = TRUE)
  
  duplicate = length(unique(bdays)) < n

  return(duplicate)
  
}

# Check whether there are duplicate birthdays in a group of 10 people
knitr::kable(birthday_sim(10), col.name = "Return Result", 
             caption = "Group Size of 10")
```

```{r}
# Run the function 10000 times for each group size between 2 and 50
sim_res = 
  expand_grid(
    n = 2:50,
    iter = 1:10000
  ) %>% 
  mutate(res = map_lgl(n, birthday_sim)) %>%
  group_by(n) %>% 
  summarize(prob = mean(res))

# Make a plot showing the probability as a function of group size
sim_res %>%
  ggplot(aes(x = n, y = prob )) + 
  geom_line() + 
  labs(
    title = "Probability of Shared Birthday vs. Group Size", 
    x = "Group Size",
    y = "Probability") +
  theme_minimal()
```

From the plot, it can be observed that the probability of at least two people sharing a birthday increases as the group size grows. When the group size is small, the probability increases gradually. However, as the group size becomes larger, the probability rises more rapidly. Eventually, the probability approaches 1 as the group size becomes sufficiently large.